A Type System for Safe and Scalable Parallelism using Logical Regions

### 2012-07-11 doc/popl2013/related.tex
Getting everything on 12 pages

Deterministic Parallel Java (DPJ) is the only other region-based parallel system of which we are
aware\cite{Bocchino09}.  While there are similarities between DPJ's effects and Legion privileges and we have
reused some DPJ notation, there are differences stemming from DPJ's static approach.
Regions in Legion are first-class and can be created, partitioned, packed, and unpacked 
dynamically, allowing programmers to compute data organization at runtime; like Sequoia, DPJ
partition schemes must be statically decided.  Legion allows 
programmers to create multiple partitions of the same region to give different 
views onto the same data, which is not possible in DPJ.  
%DPJ only supports the 
%equivalent to Legion's exclusive and atomic coherence modes \cite{Bocchino11} 
%while Legion provides safe execution even in simultaneous environments.  
There is also a difference in emphasis: DPJ requires shared memory, while Legion 
is designed for distributed heterogeneous machines.

>>>>

Deterministic Parallel Java (DPJ) is the only other region-based parallel system of which we are
aware\cite{Bocchino09}.  While there are similarities between DPJ's effects and Legion privileges, 
%and we have reused some DPJ notation, 
there are differences stemming from DPJ's static approach.
Regions in Legion are first-class and can be created, partitioned, packed, and unpacked 
dynamically, allowing programmers to compute data organization at runtime; like Sequoia, DPJ
partition schemes must be statically decided.  Legion allows 
programmers to create multiple partitions of the same region to give different 
views onto the same data, which is not possible in DPJ.  
%DPJ only supports the 
%equivalent to Legion's exclusive and atomic coherence modes \cite{Bocchino11} 
%while Legion provides safe execution even in simultaneous environments.  
There is also a difference in emphasis: DPJ requires shared memory, while Legion 
is designed for distributed heterogeneous machines.
